---
title: "Kroger, Interactive Graph"
author: "Jim Greene"
date: "June 21, 2018"
output: 
  html_document:
    code_folding: "hide"
    theme: simplex
    keep_md: true
---

```{r setup, include=FALSE}
library(dygraphs)
library(tidyquant)
library(timetk)
#kg <- tq_get("KG", "stock.prices") %>% filter(DATE >= "2013-06-21")
kg <- as.data.frame(read_csv("HistoricalQuotes.csv")[-1,])
rownames(kg) <- kg[[1]]

kg2 <- read_csv("HistoricalQuotes.csv")[-1,] %>% 
  mutate(date = ymd(date)) %>% 
  tk_xts(select = close, date_var = date)
```

</br>

### First Version with Event Lines
```{r, fig.width = 8.5}
kg[-1] %>% 
  select(close) %>% # in future could add volume to a second axis
  dygraph(main = "Kroger (KG) Stock Prices") %>%
  dyEvent("2017-06-15", "June 15 - Drop", labelLoc = "bottom") %>%
  dyEvent("2017-11-29", "November 28-30 - Rise", labelLoc = "bottom") %>%
  dyOptions(drawPoints = TRUE, pointSize = 1) %>%
  dyRangeSelector(height = 26)
```


### Second Version with Annotations
```{r, fig.width = 8.5}
kg2 %>% 
  dygraph(main = "Kroger (KG) Stock Prices") %>%
  #dyEvent("2017-06-15", "June 15 - Drop", labelLoc = "bottom") %>%
  #dyEvent("2017-11-29", "November 28-30 - Rise", labelLoc = "bottom") %>%
  dyAnnotation(x = "2017-06-15", text = "Drop", width = 30, tooltip = "June 15th, 2017: Investors React to Lowered Prices") %>%
  dyAnnotation(x = "2017-11-29", text = "Rise", width = 30, tooltip = "December 2017: Possible Reaction to Holiday Discounts") %>%
  dyOptions(drawPoints = TRUE, pointSize = 1) %>%
  dyRangeSelector(height = 26)
```


</br>
*According to [fool.com](https://www.fool.com/investing/2017/07/05/why-the-kroger-co-stock-plunged-217-in-june.aspx), investors reacted to Kroger having lowered their prices on June 15th, 2017 to provide better value to their customers.* </br>

*Around December first that same year the stock went back up. [Zacks.com](https://www.zacks.com/stock/news/284680/kroger-kr-catches-eye-stock-jumps-61) suggested that it was due to the release of the third quarter report with higher than expected revenue, but I believe that people were speculating when Kroger offered several promotions.*

