---
title: "Case Study 3, NYC Airports"
author: "Jim Greene"
date: "May 10, 2018"
output: 
  html_document:
    theme: spacelab
    keep_md: true
    code_folding: hide
---

```{r setup, include=FALSE}
library(tidyverse)
library(nycflights13)
library(pander)
```

### Background

The NYCflights13::flights dataset contains all flights departing from NYC airports in 2013 (See R Documentation). </br>
In this analysis I address two questions: </br>

#### 1. If one is leaving before noon, which two airlines would I recommend at each airport (JFK, LGA, EWR) that will have the lowest delay time at the 75th percentile?

Based on the 75th percentiles, for EWR, I reccommend Endeavor (9E) or US Airways (US); </br>
for JFK, I reccomend Delta (DL) or American Airlines (AA); </br>
and for LGA, US Airways or American Airlines.

This table shows the delays in minutes for each airline (carrier) at the 75th percentile. Negative values indicate that the plane arrived early.

```{r, eval = F, echo = F}
#This changes the formats, but I had an issue with column indexes.

flights2 <- flights

flights2$dep_time <- transmute(flights2, dep_time = sub("(\\d+)(\\d{2})", "\\1:\\2", flights2$dep_time))
#flights2$dep_time <- parse_time(flights2$dep_time, format = "%H:%M")

flights2$sched_dep_time <- transmute(flights2, sched_dep_time = sub("(\\d+)(\\d{2})", "\\1:\\2", flights2$sched_dep_time))
#flights2$sched_dep_time <- parse_time(flights2$sched_dep_time, format = "%H:%M")

flights2$arr_time <- transmute(flights2, arr_time = sub("(\\d+)(\\d{2})", "\\1:\\2", flights2$arr_time))
#flights2$arr_time <- parse_time(flights2$arr_time, format = "%H:%M")

flights2$sched_arr_time <- transmute(flights2, sched_arr_time = sub("(\\d+)(\\d{2})", "\\1:\\2", flights2$sched_arr_time))
#flights2$sched_arr_time <- parse_time(flights2$sched_arr_time, format = "%H:%M")
```

<center>
```{r, echo = T, warning = F, echo = 1:9}
JFK_delay <- filter(flights, sched_dep_time < 1200 & origin == "JFK") %>%
  group_by(carrier) %>%
  summarise(JFK = quantile(dep_delay, probs = .75, na.rm = T))

LGA_delay <- filter(flights, sched_dep_time < 1200 & origin == "LGA") %>%
  group_by(carrier) %>%
  summarise(LGA = quantile(dep_delay, probs = .75, na.rm = T))
  
EWR_delay <- filter(flights, sched_dep_time < 1200 & origin == "EWR") %>%
  group_by(carrier) %>%
  summarise(EWR = quantile(dep_delay, probs = .75, na.rm = T))

delay <- suppressMessages(plyr::join(EWR_delay, JFK_delay, type = "right"))
delay <- suppressMessages(plyr::join(delay, LGA_delay,  type = "right"))
pander(delay)
```
</center>

This plot show the distributions of delays for each carrier.

```{r, echo = T, warning = F, fig.height = 5.5}
filter(flights, sched_dep_time < 1200) %>%
  ggplot() +
  geom_violin(mapping = aes(carrier, dep_delay), fill = "#000050", color = "#000050") +
  facet_wrap( ~ origin, ncol = 1, scales = "free_x") +
  labs(x = "Carrier", y = "Departure Delays") +
  coord_cartesian(ylim = c(-20, 100)) +
  scale_y_continuous(breaks = seq(-20, 100, by = 20))
```

</br>

#### 2. Which origin airport is best to minimize one's chances of a late arrival when using Delta Airlines?

Buffalo Niagara Intl (BUF) and Cyril E. King (STT) are the least likely destinations to arrive at late.

<center>
```{r}
chance <- filter(flights, carrier == "DL" & dest != "JAC" & dest != "JAX" & dest != "PHL" & dest != "STL" & dest != "DCA" & dest != "OMA" & dest != "IND" & dest != "BNA") %>% 
  group_by(dest) %>%
  summarize(prob = mean(arr_delay > 2, na.rm = T))
#chance$`Probability of arriving later than 2 minutes` <- reorder(chance$`Probability of arriving later than 2 minutes`)
chance <- arrange(chance, prob)
colnames(chance) <- c("Destination", "Probability of arriving more than 2 minutes behind schedule")
pander(head(chance, 10))
```
</center>

```{r, echo = T, warning = F, fig.height = 7}
filter(flights, carrier == "DL" & dest != "JAC" & dest != "JAX" & dest != "PHL" & dest != "STL" & dest != "DCA" & dest != "OMA" & dest != "IND" & dest != "BNA") %>%
  ggplot() +
    theme_dark() +
    geom_hline(yintercept = seq(-40, 120, by = 20), linetype = 1, color = "#6C6C6C", size = .75) +
    geom_hline(yintercept = 0, linetype = 1, color = "#606060", size = .75) +
    geom_violin(mapping = aes(fct_reorder(dest, arr_delay), arr_delay), color = "#00D020", fill = "#00D020") +
    scale_y_continuous(breaks = seq(-40, 120, by = 10), sec.axis = dup_axis(name = NULL)) +
    coord_flip(ylim = c(-40, 120)) +
    labs(y = "Delay (Minutes)", x = "Destination", title = "Arrival Delays for Delta Airlines") + 
  theme(plot.title = element_text(hjust = 0.5))
```

```{r, eval = F, echo = F}
DL_ad <- filter(flights, carrier == "DL" & dest != "JAC" & dest != "JAX" & dest != "PHL" & dest != "STL" & dest != "DCA" & dest != "OMA" & dest != "IND" & dest != "BNA") %>%
  group_by(dest) %>%
  summarise('90th Percentile' = quantile(dep_delay, probs = .9, na.rm = T))
pander(DL_ad)
```

</br>

#### Prominent quote from "What do people do with new data"

"@hmason Interview the source, if possible, to know all of the problems with the data, use limitations, caveats, etc. — Evan Thomas Paul (@evanthomaspaul) June 12, 2014"
