---
title: "References to the Savior in The Book of Mormon"
author: "Jim Greene"
date: "June 13, 2018"
output:
  html_document:
    keep_md: true
    code_folding: hide
    theme: simplex
---

```{r setup, include=FALSE}
library(tidyverse)
library(lemon)
library(stringi)
library(rio)
library(downloader)
library(knitr)
library(scales)

# Run once:
# download("http://scriptures.nephi.org/downloads/lds-scriptures.csv.zip", "data/scriptures.zip", mode = "wb")
# unzip("data/scriptures.zip", exdir = file.path(getwd(),"data"))
# file.remove("data/scriptures.zip")

```

</br>

##### I downloaded the standard works and parsed the text of The Book of Mormon for uses of the names of Jesus Christ.
```{r, message = F}
# When running this chunk alone, this line needs to be commented out
setwd("../")

# LOAD SCRIPTURES
scriptures <- read_csv("data/lds-scriptures.csv")
bom <- scriptures %>% 
  filter(volume_short_title == "BoM")

# LOAD NAMES
names <- read_rds(gzcon(url("https://byuistats.github.io/M335/data/BoM_SaviorNames.rds")))
# Need to parse multi-word names first
names <- names %>% arrange(desc(words))
# Chosen method solve a syntax error that came up later
names_col <- names$name

# MAKE EMPTY TIBBLE
references <- tibble(name_id = character(), observation = character(), book = character())
end_observation <- ""

# FILL TIBBLE
for (book in unique(bom$book_title)) {
  scr_text <- bom %>% 
    filter(book_title == book)
  
  scr_text <- paste(c(end_observation, scr_text$scripture_text), collapse = " ")

  for (j in 1:length(names$name)) {
    scr_text <- str_replace_all(scr_text, names$name[j], str_c("__", j, "__"))
  }

  observations <- scr_text %>% 
    str_split("__[0-9]+__") %>% unlist()

  name_id <- scr_text %>% 
    str_match_all("__[0-9]+__") %>% unlist()

  references <- references %>% 
    bind_rows(tibble(name_id = name_id, observation = observations[1:length(observations) - 1], book = book))
  
  # Gets packed onto the first observation of the next book
  end_observation <- observations[length(observations)]
}

# REMOVE "__"S
references$name_id <- references$name_id %>% 
  str_extract_all("[0-9]+") %>% unlist() %>% as.integer() 

# MAKE WORD COUNT COLUMN
spaces <- rep(0, length(references$observation))
for (k in 1:(length(spaces))) {
  spaces[k] <- stri_stats_latex(references$observation[k])[["Words"]]
}

# NAMES COLUMN
references <- references %>% 
  mutate(name = names_col[name_id], observation_id = c(1:length(spaces)), space = spaces)

# REORDER BOOK FACTORS TO FIX COLOR LEGEND
references$book <- factor(references$book, levels = unique(references$book))
```

</br>

##### The Savior is mentioned over 4000 times in the Book of Mormon. Each point in the plot below represents the group of words between each reference; they are plotted in order from left to right. The outliers are what most stand out.
```{r, fig.width = 10, fig.height = 8, figure.align = "center"}
my_colors <- c("indianred","chocolate4","purple","#ff8800","mediumblue","#00d000","#bb0000","#229977","darkgoldenrod2","#cc33cc","olivedrab","#00cccc","darkmagenta","aquamarine3","#ee7539")

references %>% 
  ggplot(aes(x = observation_id, y = space)) +
  theme_bw() +
  annotate(geom = "text", x = 2737, y = 4038, label = "Alma 50:39 - 53:10", size = 2.5, hjust = 0) +
  annotate(geom = "text", x = 2830, y = 2402, label = "Helaman 1:11 - 3:20", size = 2.5, hjust = 0) +
  annotate(geom = "text", x = 2820, y = 1735, label = "Alma 62:3 - 62:41", size = 2.5, hjust = 0) +
  annotate(geom = "text", x = 1538, y = 1703, label = "Mosiah 19:2 - 20:21", size = 2.5, hjust = 1) +
  annotate(geom = "text", x = 2595, y = 1539, label = "Alma 46:41 - 47:36", size = 2.5, hjust = 1) +
  annotate(geom = "text", x = 3075, y = 1468, label = "3 Nephi 8:1 - 9:15", size = 2.5, hjust = 0) +
  annotate(geom = "text", x = 3830, y = 1219, label = "Ether 13:20 - 14:24", size = 2.5, hjust = 1) +
  annotate(geom = "text", x = 150, y = 905, label = "1 Nephi 8:9 - 36", size = 2.5, hjust = 0) +
  annotate(geom = "text", x = 1130, y = 592, label = "Jacob 5:57 - 70", size = 2.5, hjust = 1) +
  geom_point(aes(color = book)) +
  scale_color_manual(values = my_colors) +
  labs(x = "", y = "Number of words between each reference", title = "References to Jesus Christ in the Book of Mormon", color = "") +
  scale_y_continuous(breaks = seq(0, 4000, by = 200)) +
  theme(legend.position = "bottom", legend.text = element_text(size = 12)) +
  guides(color = guide_legend(nrow = 2))
```

</br>

##### This plot was created to get a better view of the individual observations. In this plot it is easier to notice the pattern changes between stories and authors.
```{r, warning = F, fig.width = 10, fig.height = 7.25, figure.align = "center"}
references %>% 
  ggplot(aes(x = observation_id, y = space, color = book)) +
  theme_bw() +
  geom_point() +
  scale_color_manual(values = my_colors) +
  labs(x = "", y = "Number of words between each reference (log 10 scale)", title = "References to Jesus Christ in the Book of Mormon", color = "") +
  scale_y_log10(breaks = c(0,1,2,3,5,10,15,30,50,100,150,300,500,1000,2000,3000,4000)) +
  theme(legend.position = "bottom", panel.grid.minor = element_blank(), legend.text = element_text(size = 12)) +
  scale_x_continuous(breaks = c()) +
  guides(color = guide_legend(nrow = 2))
  
```


```{r}
references_2 <- references %>% left_join(names, by = "name")
references_2 <- references_2 %>% mutate(cumulative_words = rep(space[1], length(space)))
# references_2$space <- as.integer(references_2$space)
# references_2$cumulative_words <- as.integer(references_2$cumulative_words)

for (p in 2:length(references_2$cumulative_words)) {
  references_2$cumulative_words[p] <- (references_2$space[p] + references_2$cumulative_words[p - 1] + references_2$words[p - 1])
}
```

</br>

##### Realizing that the previous graphs are somewhat deceptive, I created this which shows the actual distance in words between each reference. I also show the length of each reference by changing the size of the points. As a result, this is much more what the Book of Mormon actually looks like, at least in terms of references to Christ.
```{r, warning = F, fig.width = 10, fig.height = 7.5, figure.align = "center"}
references_2 %>% 
  ggplot(aes(x = cumulative_words, y = space, color = book, size = words)) +
  theme_bw() +
  geom_point(aes(), alpha = 0.75) +
  scale_color_manual(values = my_colors) +
  labs(x = "\nTotal number of words before each name", y = "Number of words between each reference (log 10 scale)", title = "References to Jesus Christ in the Book of Mormon", color = "", size = "Number of words in name") +
  scale_y_log10(breaks = c(0,1,2,3,5,10,15,30,50,100,150,300,500,1000,2000,3000,4000)) +
  theme(legend.position = "bottom", legend.box = "vertical", panel.grid.minor = element_blank(), legend.text = element_text(size = 12)) +
  scale_x_continuous(position = "top", labels = comma, breaks = seq(0, 300000, by = 25000)) +
  guides(color = guide_legend(nrow = 2, order = 1), size = guide_legend(order = 2)) +
  scale_size_continuous(range = c(1, 3))
```


```{r, echo = F, eval = F, warning = F, fig.width = 10, fig.height = 7.25, figure.align = "center"}
# this is just code for a different graphic I chose not to include.
references_2 %>% 
  ggplot(aes(x = cumulative_words, y = space, color = book, alpha = 0.05)) + # size = (words)
  theme_bw() +
  geom_point() +
  scale_color_manual(values = my_colors) +
  labs(x = "Total number of words before each name", y = "Number of words between each reference", title = "References to Jesus Christ in the Book of Mormon", color = "", size = "Number of words in reference") +
  scale_y_continuous(breaks = seq(0, 4000, by = 200)) +
  theme(legend.position = "bottom", panel.grid.minor = element_blank(), legend.text = element_text(size = 12)) +
  scale_x_continuous(breaks = c()) +
  guides(color = guide_legend(nrow = 2))
```

</br>

##### This was a prototype graphic that zooms in on the 0-300 range, instead of using a log scale. I had received a lot of feedback from students who didn't like the log scale, but those with experience in data visualization stated since that my log scale is good.
```{r, eval = T, warning = F, fig.width = 10, fig.height = 7.25, figure.align = "center"}
references_2 %>% 
  ggplot(aes(x = cumulative_words, y = space, color = book)) + # size = (words)
  theme_bw() +
  geom_point() +
  scale_color_manual(values = my_colors) +
  labs(x = "Total number of words before each reference", y = "Number of words between each name", title = "References to Jesus Christ in the Book of Mormon", color = "", size = "Number of words in name") +
  scale_y_continuous(limits = c(0,300), breaks = seq(0, 300, by = 20)) +
  scale_x_continuous(labels = comma, breaks = seq(0, 300000, by = 25000)) +
  theme(legend.position = "bottom", panel.grid.minor = element_blank(), legend.text = element_text(size = 12)) +
  guides(color = guide_legend(nrow = 2))
```



```{r, warning = F}
names %>% 
  arrange(words) %>% 
  select(name) %>%
  kable(caption = "Here are the names that were included in the search:", row.names = 1:nrow(names))
```
